This is my paper title

### 2023-04-03 outputs/paper/paper.qmd
Correcting fig-3

#### Quarto workspace setup and reading csv's into quarto ####
library(tidyverse)
library(palmerpenguins)
library(haven)
library(here)

@@

clean_data_degree |>
  ggplot(aes(x = degree)) +
  geom_bar(fill = "slateblue1") +
  theme_minimal() +
  labs(x = "Degree Obtained",
       y = "Number of Respondents",
       title = "Degree obtained by respondents")
```

@@

@@

\newpage
Talk way more about it.

@@

```{r}
#| label: fig-5
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4

>>>>

#### Quarto workspace setup and reading csv's into quarto ####
library(tidyverse)
library(palmerpenguins)
library(haven)
library(here)
library(dplyr)

@@

clean_data_degree$degree <-
  factor(degrees_clean$degree,
         levels = c("< High School", "High School", "Junior College", "Bachelors", "Graduate"))

degree_obtained |>
  ggplot(aes(x = degree, y = freq)) +
  geom_col(fill = "slateblue1") +
  theme_minimal() +
  labs(x = "Degree Obtained",
       y = "Number of Respondents",
       title = "Degree obtained by respondents")
```

@@

clean_data_willingness$grnprice <-
  factor(willingness_clean$grnprice,
         levels = c("Very Unwilling", "Fairly Unwilling", "Neutral", "Fairly Willing", "Very Willing"))

@@

@@
